Index measures for oak decline severity using phenotypic descriptors

### 2019-11-11 manuscript/manuscript.Rmd
added phenotypic descriptor table
output format change to pdf_document2

---
title: "Indexes measures for oak decline severity using phenotypic descriptors"
output: pdf_document
keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = TRUE,warning = FALSE,message = FALSE)
```

@@

@@

@@

@@

@@

## Checks

```{r check,comment=''}
source('../code/check.R')
manuscript_check()
```

## References

>>>>

---
title: "Index measures for oak decline severity using phenotypic descriptors"
output: 
  bookdown::pdf_document2:
   toc: false
   number_sections: false
keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      cache = TRUE,
                      fig.pos = 'H',
                      warning = FALSE,
                      message = FALSE)
```

@@

Oak decline syndromes are facilitated by a variety of both biotic and abiotic factors

@@

R v`r str_c(version$major,version$minor,sep ='.')` was used for all parsing, preparation and analysis of phenotypic data.

@@

Large phenotypic differences were found between the sites by supervised random forest (Figure \@ref(fig:siteLocations))

@@

\newpage
## Tables

```{r tables,child='tables.Rmd'}
```

\newpage
## Figures

\newpage
## Checks

@@

```{r figures,child='figures.Rmd'}

```

```{r check,comment='',cache=FALSE}
source('../code/check.R')
manuscript_check()
```

\newpage
## References
